Chum Populations

### 2015-10-13 paper/main.tex
update paper

\usepackage{fontspec}
\setmainfont{Georgia}
%\setsansfont{Trebuchet MS}
%\setmonofont{Inconsolata}

@@

\subsection*{Intro wrap-up / Objectives}

@@

\subsection*{Sequence analysis}
Genetic variation was quantified with a reference-based approach using the \texttt{Stacks} software pipeline \citep{Catchen2013}.  A chum salmon reference constructed from \citep{Waples2015}. Reads from each individual were aligned to the reference with BWA-mem  (version 0.7.5a-r405) \citep{Li2013}.  Alignments containing indels or with a mapping quality (MAPQ) < 20 were removed. Stacks components \texttt{pstacks}, \texttt{cstacks}, \texttt{sstacks}, and \texttt{populations} were used to identify and genotype genetic variants for each population individual.  See supplemental file XXX for detailed description of the analysis pipeline.

PLINK (version v1.90b3q) \citep{Chang2014} was used to filter genotypes.  Loci or individuals with more than 25\% missing data were removed.  Loci with a minor allele frequency below 5\% were removed. Hardy-Weinberg equilibrium was tested within each collection using the mid p-value statistic \citep{Graffelman2013}. Loci rejecting HWE in more than 5 collections were removed.  Finally, within each RAD locus, only the single SNP with the largest minor allele frequency was retained, to reduced pseudo-replication caused by physical linkage.  Note that for for the dominant coding used for the PCA analyses of population structure (see below), sequence haplotypes containing all SNPs within each locus were utilized.

@@

\subsection*{Population-based analyses}

MAF, Heterozygosity

phylogenetic tree

Genome scan - gloabal or paired populations -

Fst across the genome.  Use LOESS (local regression) to reveal regions of elevated differentiation.  Benefits of this approach vs a bootstrapping methods (eg. Hohenlohe 2010)

Effective population size was estimated for each population using the LD method implemented in the LDNe software package \citep{Waples2010}.  The LD methods estimates average correlation of alleles at pairs of loci (r2). The mean pairwise r2 value across unlinked loci provides an estimate of contemporary effective population size. The linkage map was used to ensure that only pairs of loci not co-located on a chromosome were used to calculate mean r2.

@@

Formal tests for population structure \citep{Patterson2006}, based on the Tracey-Widom distribution \citep{Tracy1994}.

\subsection*{Linkage map}

We constructed a consensus linkage map from three gynogenetic haploid families (sizes 175, 34, 31) with the  LEPmap \citep{Rastas2013}. This linkage map  builds on the map presented in \citet{Waples2015} with the addition of two additional families and the placement of centromeric regions. As the linkage map is constructed from gynogenetic haploid offspring, it only reflects recombination events that occur within the female lineage. As with many other species, there are sex-specific differences in recombination rates. (Not sure what else to say about female/male differences in linkage maps). The position of centromeres within each chromosome will be estimated by measuring recombination fractions along chromosomes (cite Limborg?).

@@

\section*{Results}

Genotyping rate
\subsection*{Population-based}
population structure

@@

\begin{figure}[H]
\includegraphics[scale=.3]{figures/supplemental/ascertainment.png}
\caption{Minor allele frequency (MAF) density histograms for all loci (blue) and the subset of loci placed on the linkage map (green). The rightward shift in the MAF distribution shows the effect of ascertainment bias.} \textbf{TODO: align histogram bins, check the .5 boundary}
\end{figure}

@@

Of the xxx loci scored in wild collectionsm, xxx were placed on the linkage map, and covering all LGs.

A total of xxx paralogs were identified and placed onto the linkage map.  The location of these paralogs were were concentrated on the distal ends of three chromosomes, consistent with results found in other Salmonid species  \citep{Brieuc2014, Kodama2014, Waples2015} (also McKinney submitted). Consistency across families (see supplemental table xx)

>>>>

%\usepackage{fontspec}
%\setmainfont{Georgia}
%\setsansfont{Trebuchet MS}
%\setmonofont{Inconsolata}

@@

\subsection*{Objectives}

@@

\subsection*{Sequence analysis}
Genetic variation was quantified with a reference-based approach using the \texttt{Stacks} software pipeline \citep{Catchen2013}.  A chum salmon reference constructed from \citep{Waples2015}. Reads from each individual were demultiplexed and quality filtered with 'process-radtags' and then aligned to the reference with BWA-mem  (version 0.7.5a-r405) \citep{Li2013}.  Alignments containing indels or with a mapping quality < 20 were removed. Stacks components \texttt{pstacks}, \texttt{cstacks}, \texttt{sstacks}, and \texttt{populations} were used to identify and genotype genetic variants for each population individual.

The initial set of genotypes and individuals was assessed prior to further analysis.  Loci or individuals with more than 25\% missing data were removed.  Loci with a minor allele frequency below 5\% were removed. Hardy-Weinberg equilibrium was tested within each collection using the mid p-value statistic \citep{Graffelman2013}. Loci rejecting HWE in more than 5 collections were removed.  Finally, within each RAD locus, only the single SNP with the largest minor allele frequency was retained, to reduced pseudo-replication caused by physical linkage.  All filters were applied in PLINK (version v1.90b3q) \citep{Chang2014}. Note that for for the dominant coding used for the PCA analyses of population structure (see below), sequence haplotypes containing all SNPs within each locus were utilized. See supplemental file XXX for detailed description of the analysis pipeline.

@@

\subsection*{Linkage map}
We constructed a consensus linkage map from three gynogenetic haploid families (sizes 175, 34, 31) with the  LEPmap \citep{Rastas2013}. This linkage map  builds on the map presented in \citet{Waples2015} with the addition of two additional families and the placement of centromeric regions. As the linkage map is constructed from gynogenetic haploid offspring, it only reflects recombination events that occur within the female lineage. As with many other species, there are sex-specific differences in recombination rates. (Not sure what else to say about female/male differences in linkage maps). The position of centromeres within each chromosome will be estimated by measuring recombination fractions along chromosomes (cite Limborg?).

@@

Formal tests for population structure \citep{Patterson2006}, based on the Tracey-Widom distribution \citep{Tracy1994}. Q values.

\subsection*{Population-based analyses \& genome scans}
Allele frequencies, Heterozygosity, and Fst (Weir 1984) were calculated for each locus in PLINK.

Fst across the genome.  Use LOESS (local regression) to reveal regions of elevated differentiation.  Benefits of this approach vs a bootstrapping methods (eg. Hohenlohe 2010).

Genome scans.  Bayescan all populations - 
LFMM models with run-timing data

Effective population size was estimated for each population using the LD method implemented in the LDNe software package \citep{Waples2010}.  The LD methods estimates the average correlation of alleles at pairs of loci (r2). The mean pairwise r2 value across independently-assorting loci provides an estimate of contemporary effective population size. Only loci placed on the linkage map were used for this calculation and the map was utilized to ensure that only pairs of loci not co-located on a chromosome contributed to mean r2.

@@

\subsection*{Should I do?}
phylogenetic tree

\section*{Results}
\subsection*{Sequencing and genotyping}
table of sequencing results -  by collection location, including family and wild samples.
Genotyping rate

\subsection*{Individual-based}

\subsection*{Population-based}
population structure

@@

\begin{figure}[H]
\includegraphics[scale=.3]{figures/supplemental/ascertainment2.png}
\caption{Minor allele frequency (MAF) density histograms for all loci (blue) and the subset of loci placed on the linkage map (green). The rightward shift in the MAF distribution shows the effect of ascertainment bias.} \textbf{TODO: align histogram bins, check the .5 boundary}
\end{figure}

@@

Of the 13,407 loci scored in the wild, 6,251 were placed on the linkage map.

A total of xxx paralogs were identified and placed onto the linkage map (do I want to count them in pairs or not?).  The location of these paralogs were were concentrated on the distal ends of three chromosomes, consistent with results found in other Salmonid species  \citep{Brieuc2014, Kodama2014, Waples2015} (also McKinney submitted). Consistency across families (see supplemental table xx)
